Self Regulation Ontology Retest Data: Initial Exploration

### 2017-02-22 SRO_Retest_Analyses.Rmd
cont working on retest exploration

Apply the same cleaning procedure that was used for meaningful vars for all vars:
```{r}
transform_remove_skew = function(data, threshold = 1){
}
```

>>>>

Apply the same cleaning procedure that was used for meaningful vars for all vars:
```{r}
"%w/o%" <- function(x, y) x[!x %in% y]

transform_remove_skew = function(data, cols, threshold = 1){

  tmp = as.data.frame(apply(data[,columns],2,skew))
  names(tmp) = c("skew")
  tmp$dv = row.names(tmp)
  tmp = tmp %>% 
    filter(abs(skew)>threshold)

  skewed_variables = tmp$dv
  skew_subset = data[, skewed_variables]
  positive_subset = data[,tmp$dv[tmp$skew>0]]
  negative_subset = data[,tmp$dv[tmp$skew<0]]

  # transform variables
  # log transform for positive skew
  positive_subset = log(positive_subset)
  successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
  names(successful_transforms) = c('skew')
  successful_transforms$dv = row.names(successful_transforms)
  successful_transforms = successful_transforms %>% filter(abs(skew)<threshold)
  successful_transforms = successful_transforms$dv
  successful_transforms = positive_subset[,successful_transforms]
  dropped_vars = names(positive_subset) %w/o% names(successful_transforms)

  # replace transformed variables
  data = data[,-c(which(names(data) %in% names(positive_subset)))]
  names(successful_transforms) = paste0(names(successful_transforms), '.logTr')
  print.noquote(rep('*', 40))
  print(paste0('Dropping', length(dropped_vars) ,'positively skewed data that could not be transformed successfully:')

  print('\n'.join(dropped_vars))
  print.noquote(rep('*', 40))
  data = pd.concat([data, successful_transforms], axis = 1)
}

tmp = as.data.frame(apply(retest_data[, matching_dv_columns], 2, skew))
names(tmp) = c('skew')
tmp$dv = row.names(tmp)
tmp = tmp %>%
  filter(abs(skew)>1)
positive_subset = retest_data[,tmp$dv[tmp$skew>0]]

positive_subset = log(positive_subset)
successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
names(successful_transforms) = c('skew')
successful_transforms$dv = row.names(successful_transforms)
successful_transforms = successful_transforms %>% filter(abs(skew)<1)
successful_transforms = successful_transforms$dv
successful_transforms = positive_subset[,successful_transforms]
dropped_vars = names(positive_subset) %w/o% names(successful_transforms)

tmp_retest_data = retest_data
tmp_retest_data = tmp_retest_data[,-c(which(names(tmp_retest_data) %in% 
                                              names(positive_subset)))]

#transform_remove_skew(retest_data, matching_dv_columns)
```
